SunPy - Python for Solar Physics

### 2014-08-28 3-4-Helioviewer.tex
helioviewer section cleaned up

SunPy provides the ability to download images hosted by the
Helioviewer Project (\url{http://helioviewer.org}).  
The aim of the Helioviewer Project is to enable
the exploration of solar and heliospheric data from multiple data
sources (such as instrumentation and feature/event catalogues) via
easy-to-use visual interfaces. The Helioviewer Project have developed two client 
applications that allow users to browse images and create movies of the Sun taken 
by a variety of instruments: \url{http://www.helioviewer.org}, a 
Google Maps-like web application, and \url{http://www.jhelioviewer.org}, 
a movie streaming desktop application. In order to manage all of this data, the Helioviewer
project maintains archives of all of its data in JPEG2000 format (for further
details on the Helioviewer Project, see \citealt{muller2009}). The
JPEG2000 files are typically highly compressed compared to the source
FITS files from which they are generated, but are still high-fidelity, and thus can be used to quickly
visualise large amounts of data from multiple sources.  SunPy is
also used in Helioviewer production servers to manage the download and
ingestion of JPEG2000 files from remote servers.

The Helioviewer Project categorises image data based on the physical
construction of the source instrument, using a simple hierarchy:
observatory $\rightarrow$ instrument $\rightarrow$ detector
$\rightarrow$ measurement, where '$\rightarrow$' means 'provides
(possibly multiple)'.  
%schriste - say what?!
Each Helioviewer Project JPEG2000 file contains
metadata which are based on the original FITS header
information, and carry sufficient information to permit overlay with
other Helioviewer JPEG2000 files. Images can be accessed either as
PNGs (Section \ref{sssec:hv:png}) or as JPEG2000 files (Section
\ref{sssec:hv:jp}).

>>>>

SunPy provides the ability to download images hosted by the
Helioviewer Project (\url{http://wiki.helioviewer.org}).  
The aim of the Helioviewer Project is to enable
the exploration of solar and heliospheric data from multiple data
sources (such as instrumentation and feature/event catalogues) via
easy-to-use visual interfaces. The Helioviewer Project have developed two client 
applications that allow users to browse images and create movies of the Sun taken 
by a variety of instruments: \url{http://www.helioviewer.org}, a 
Google Maps-like web application, and \url{http://www.jhelioviewer.org}, 
a movie streaming desktop application. The Helioviewer
project maintains archives of all its image data in JPEG2000 format (\citealt{muller2009}). The
JPEG2000 files are typically highly compressed compared to the source
FITS files from which they are generated, but are still high-fidelity, and thus can be used to quickly
visualise large amounts of data from multiple sources.  SunPy is
also used in Helioviewer production servers to manage the download and
ingestion of JPEG2000 files from remote servers.

The Helioviewer Project categorises image data based on the physical
construction of the source instrument, using a simple hierarchy:
observatory $\rightarrow$ instrument $\rightarrow$ detector
$\rightarrow$ measurement, where ``$\rightarrow$'' means ``provides a''.  
%schriste - say what?!
Each Helioviewer Project JPEG2000 file contains
metadata which are based on the original FITS header
information, and carry sufficient information to permit overlay with
other Helioviewer JPEG2000 files. Images can be accessed either as
PNGs (Section \ref{sssec:hv:png}) or as JPEG2000 files (Section
\ref{sssec:hv:jp}).
